Enhancing Depth Estimation with Iterative Stereo-LiDAR Fusion: An Application of the Papoulis-Gerchberg Algorithm\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-10 paper/icra2025/main.tex
CoDIT paper forked as ICRA init

\section{Experiment}

\subsection{Experimenting our Algorithm With Kitti Benchmark Suite}
%% Mention the dataset preparation picking data from different datasets

@@

\subsubsection{Sensor Suit}
We conducted experiments using the data we collected from our sensors. We used Velodyne VLP-16 as 3D LiDAR and Zed Stereo Camera as main sensing devices. We also developed a suit that mounts the sensors we use for experimenting in fixed positions. The sensor suit has also an Nvidia Jetson Nano 4GB computer. The computer plays different roles in different experiment scenarios.
% put images of sensor suit only
To obtain real-life like conditions by mounting the sensor suit on top of a quadruped robot. 
% put images of sensor suit with robot
\paragraph{Upsampling of LiDAR Data}
%% Further improvements dynamic LiDAR upsampling with kalman

\subsubsection{Experiment Scenarios}
\paragraph{Cloud Computing (Performance):}
\paragraph{Mobile Computing (Performance):}
\paragraph{SLAM (Quality):}
% Put three slam maps and visual odometry visualization images {Only Stereo}, {Only Lidar}, {Fused}. AIM:Compare map quality and odomerty accuracy.

@@

>>>>

\section{Experiment}
To test the performance and quality of our work, we developed some test methods. Although there are widely used datasets to test the stereo and flow depth estimation algorithms, due to the fundamental difference between well known depth estimation algorithms and our work, we had to design custom tests and benchmarks.
The traditional depth estimation algorithms are mainly focuses on generating disparity maps using stereo pair or flow image pairs, the datasets and benchmarks provide stereo pairs as input data and LiDAR measurements as ground truth. Unlike a standard depth estimation method, our multi-sensory system uses also the LiDAR measurements to predict depth.
We designed different tests to both compare our method with traditional single sensory methods and test it with real life conditions.
\subsection{Experimenting our Algorithm With KITTI Benchmark Suite}
The KITTI Vision Benchmark Suite is a well-established resource for researchers and developers working on computer vision algorithms, particularly those related to autonomous driving. It provides a diverse set of datasets and evaluation tools for various tasks, including:

\paragraph{Stereo vision:} This involves reconstructing 3D information from two slightly different camera viewpoints. KITTI offers datasets for both static and dynamic scenarios.
\paragraph{Optical flow:} This measures the apparent motion of pixels between consecutive video frames, which is crucial for tasks like motion estimation and scene understanding.
\paragraph{Visual odometry:} This estimates the 3D motion of a camera solely based on visual information, which is essential for robot navigation.
3D object detection and tracking: This involves identifying and locating objects of interest (e.g., cars, pedestrians) in 3D space, while tracking their movement over time.
The suite leverages data captured from a specially equipped vehicle driving in various environments, including urban streets, rural areas, and highways. This data includes:

High-resolution color and grayscale camera images
Velodyne laser scanner data (LiDAR) for accurate depth information
GPS localization data
Researchers can use the KITTI datasets to train and evaluate their algorithms, and compare their performance against others on the provided leaderboards. This fosters advancements in computer vision techniques with real-world applications, particularly in the field of autonomous driving.
%% Mention the dataset preparation picking data from different datasets

@@

\subsubsection{Sensor Suit}
We conducted experiments using the data we collected from our sensors. We used Velodyne VLP-16 as 3D LiDAR and Zed Stereo Camera as main sensing devices. We also developed a suit that mounts the sensors we use for experimenting in fixed positions. The sensor suit has also an Nvidia Jetson Nano 4GB computer. The computer plays different roles in different experiment scenarios.
% put images of sensor suit only
To obtain real-life like conditions by mounting the sensor suit on top of a quadruped robot.
% put images of sensor suit with robot

\subsubsection{Experiment Scenarios}
We conducted different experiment scenarios to measure different metrics.
\paragraph{Cloud Computing (Performance):}
In  this scenario, the 
\paragraph{Mobile Computing (Performance):}
\paragraph{SLAM (Quality):}
% Put three slam maps and visual odometry visualization images {Only Stereo}, {Only Lidar}, {Fused}. AIM:Compare map quality and odomerty accuracy.

@@

\subsection{Results Obtained From KITTI Benchmark Suite Experiments}

\begin{table}[htbp]
    \caption{Evaluation of our method and standard mono-sensory methods}
    \begin{center}
        \begin{tabular}{|c|c|c|}
            \hline
            \textbf{Table}&\multicolumn{2}{|c|}{\textbf{Metrics}} \\
            \cline{2-3} 
            \textbf{Head} & \textbf{\textit{MAe}}& \textbf{\textit{RMSe}} \\
            \hline
            Stereo Depth& &   \\
            \hline
            LiDAR Measurement& More table copy$^{\mathrm{a}}$& \\
            \hline
            Ours& More table copy$^{\mathrm{a}}$& \\
            \hline
            \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
        \end{tabular}
        \label{tab1}
    \end{center}
\end{table}

\subsection{Results Obtained From Sensor Suit Experiments}

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}
